---
title: "Week 3 - Prediction Model"
author: "Pedro Boareto"
date: "24/07/2020"
output: html_document
---
**Libraries**
```{r}
library(e1071)
```

**Loading preview data**
```{r}
# load the trigram data
load("df_trigram.RData")
```

**Presetting Algorithm**
```{r}
Bayes <- naiveBayes(Y ~ X1 + X2, df_tri)
save(Bayes, uni_levels, file = "Bayes.RData")
```

**Testing Prediction**
```{r}
string <- "I love"  # Input test variable
split <- strsplit(string, split = " " )# split it into separate words
factor <- factor(unlist(split), levels=uni_levels)# encode as a factor using the same levels
df <- data.frame(X1 = factor[1], X2 = factor[2])# transform to data frame
pred <- predict(Bayes, df)# estimate using the model
pred <- as.character(pred)
pred
```

**Questions**
1. How does the model perform for different choices of the parameters and size of the model?
2. How much does the model slow down for the performance you gain?
3. Does perplexity correlate with the other measures of accuracy?
4. Can you reduce the size of the model (number of parameters) without reducing performance?