---
title: "Week 2 - Exploratory Analysis and Modelling"
author: "Pedro Boareto"
date: "23/07/2020"
output: html_document
---
#Exploratory Analysis
**Libraries**
```{r}
library(stringi); library(ggplot2)
```
**Basic Exploratory Analysis - Blogs**
```{r}
summary(nchar(blogs))
stats_blogs   <- stri_stats_general(blogs)
words_blogs   <- stri_count_words(blogs)
summary(words_blogs)
```
**Basic Exploratory Analysis - News**
```{r}
summary(nchar(news))
words_news <- stri_count_words(news)
stats_news <- stri_stats_general(news)
summary(words_news)
```
**Basic Exploratory Analysis - Twitter**
```{r}
summary(nchar(twitter))
stats_twitter <- stri_stats_general(twitter)
words_twitter <- stri_count_words(twitter)
summary(words_twitter)
```

**questions**
01. Some words are more frequent than others - what are the distributions of word frequencies?
02. What are the frequencies of 2-grams and 3-grams in the dataset?
03. How many unique words do you need in a frequency sorted dictionary to cover 50% of all word instances in the language? 90%?
04. How do you evaluate how many of the words come from foreign languages?
05. Can you think of a way to increase the coverage -- identifying words that may not be in the corpora or using a smaller number of words in the dictionary to cover the same number of phrases?

#Modelling - PART 1
**Libraries**
```{r}
library(tm); library(RWeka); library(dplyr); library(magrittr)
```
**Loading Files**
```{r}
# load data
load("blogs.RData"); load("news.RData"); load("twitter.RData"); load("sample_blogs.RData"); load("sample_news.RData"); load("sample_twitter.RData")
```
**Corpus construct - Blogs**
```{r}
# contruct single corpus from sample data
sample_blogs <- data.frame(sample_blogs)
sample_blogs <- sample_blogs %>% mutate(doc_id = row_number())
sample_blogs <- sample_blogs[c("doc_id","sample_blogs")]
sample_blogs <- rename(sample_blogs,text=sample_blogs)
sample_blogs <- DataframeSource(sample_blogs)
sample_blogs <- VCorpus(sample_blogs)
vc_blogs <- tm_map(sample_blogs, stripWhitespace)
```
**Corpus construct - News**
```{r}
sample_news <- data.frame(sample_news)
sample_news <- sample_news %>% mutate(doc_id = row_number())
sample_news <- sample_news[c("doc_id","sample_news")]
sample_news <- rename(sample_news,text=sample_news)
sample_news <- DataframeSource(sample_news)
sample_news <- VCorpus(sample_news)
vc_news <- tm_map(sample_news, stripWhitespace)
```
**Corpus construct - Twitter**
```{r}
sample_twitter <- data.frame(sample_twitter)
sample_twitter <- mutate(sample_twitter, doc_id = row_number())
sample_twitter <- sample_twitter[c("doc_id","sample_twitter")]
sample_twitter <- rename(sample_twitter,text=sample_twitter)
sample_twitter <- DataframeSource(sample_twitter)
sample_twitter <- VCorpus(sample_twitter)
vc_twitter <- tm_map(sample_twitter, stripWhitespace)
```
**Mergeing Corpus**REVER ###############################
```{r}
######save(sample_blogs, sample_news, sample_twitter, file= "sample_data.RData") #USA MESMO??????????
vc_all <- c(vc_blogs, vc_news, vc_twitter)
```

#Modelling - PART 2
**Createing Bi-gram token** REVER ###############################
```{r}
##### ngram tokaniser
#####bigram_token <- function(x) NGramTokenizer(x, Weka_control(min = 2L, max = 2L))
```
**Createing Tri-gram token**
```{r}
trigram_token <- function(x) NGramTokenizer(x, Weka_control(min = 3L, max = 3L))
```
**aaaaaaaaaaaaaaaaaaaaaaaaa** REVER ###############################
```{r}
# check length function
length_is <- function(n) function(x) length(x)==n #USA MESMO??????????
```
**Makeing unigram levels**
```{r}
# frequency unigrams
tdm_unigram <- vc_all %>% TermDocumentMatrix(control = list(removePunctuation = TRUE, removeNumbers = TRUE, wordLengths = c( 1, Inf)))
freq_unigram <- tdm_unigram %>% as.matrix %>% rowSums
# write all unigrams to a list
# in order to create uniform levels of factors
unigram_levels <- unique(tdm_unigram$dimnames$Terms)
```
**Makeing trigram levels**
```{r}
# trigram Term-Document Matrix
tdm_trigram <- vc_all %>% TermDocumentMatrix(control = list(removePunctuation = TRUE, removeNumbers = TRUE, wordLengths = c( 1, Inf), tokenize = trigram_token))
# aggregate frequencies
tdm_trigram %>% as.matrix %>% rowSums -> freq_trigram
# repeat by frequency
freq_trigram %<>% names %>% rep(times = freq_trigram)
# split the trigram into three columns
freq_trigram %<>% strsplit(split=" ")
# filter out those of less than three columns
freq_trigram <- do.call(rbind, Filter(length_is(3), freq_trigram))
# transform to data.frame encode as factors
df_trigram <- data.frame(X1 = factor(freq_trigram[,1], levels = unigram_levels),X2 = factor(freq_trigram[,2], levels = unigram_levels),Y  = factor(freq_trigram[,3], levels = unigram_levels))
```
**Saving n-grans for prediction**
```{r}
# save data frame
save(df_trigram, unigram_levels, file = "df_trigram.RData")
```

**Questions**
06. How can you efficiently store an n-gram model (think Markov Chains)?
07. How can you use the knowledge about word frequencies to make your model smaller and more efficient?
08. How many parameters do you need (i.e. how big is n in your n-gram model)?
09. Can you think of simple ways to "smooth" the probabilities (think about giving all n-grams a non-zero probability even if they aren't observed in the data) ?
10. How do you evaluate whether your model is any good?
11. How can you use backoff models to estimate the probability of unobserved n-grams?
